Table 1

### 2017-06-30 doc/RMD/table-1.Rmd
update sorting for table 1

```{r isolate_table, results = "asis"}
library("readr")
library("dplyr")
library("huxtable")

clmn <- cols(
  .default = col_integer(),
  Region = col_character(),
  Source = col_character(),
  Host = col_character()
)

@@

dat <- readr::read_csv(file.path(PROJHOME, "data/clean_data.csv"), col_types = clmn) %>%
  mutate(Country = ifelse(nchar(Region) == 2, "USA", Region)) %>% # Defining country column
  mutate(Region = ifelse(nchar(Region) == 2, Region, "")) %>%     # Adding blanks for international "states"
  select(Country, Region, Source, Year, Host) %>%                 # Summarizing the number of isolates
  group_by_all() %>%                                              #
  summarize(N = n()) %>%                                          #
  arrange(desc(Country), Region, Source, Year) %>%                # Rearranging rows
  group_by(Country, Region, Source) %>%                           # Collapsing Years and Hosts
  summarize(Year = paste(sort(unique(Year)), collapse = ", "),     #
            Host = paste(sort(unique(Host)), collapse = ", "),    #
            N = sum(N)) %>%                                       #
  arrange(desc(Country), Region, Source, N) %>%                   # Rearranging rows
  group_by(Country, Region) %>%                                   # Adding blanks in repeated Country and Region Names
  mutate(set_blank = blank_it(Region)) %>%                        #
  ungroup() %>%                                                   #
  mutate(Country = ifelse(set_blank, "", Country)) %>%            #
  mutate(Region = ifelse(set_blank, "", Region)) %>%              #
  select(Country, Region, Source, Year, Host, N) %>%              #
  rename(State = Region) %>%                                      # Renaming columns
  rename(`Field Code` = Source)                                   #

>>>>

```{r load_packages, warnings = FALSE, messages = FALSE}
library("readr")
library("dplyr")
library("huxtable")
```

```{r isolate_table, comment = NA}
clmn <- cols(
  .default = col_integer(),
  Severity = col_double(),
  Region = col_character(),
  Source = col_character(),
  Host = col_character()
)

@@

dat <- readr::read_csv(file.path(PROJHOME, "data/clean_data.csv"), col_types = clmn) %>%
  mutate(Country = ifelse(nchar(Region) == 2, "USA", Region)) %>% # Defining country column
  mutate(Region = ifelse(nchar(Region) == 2, Region, "-")) %>%     # Adding blanks for international "states"
  select(Country, Region, Source, Year, Host) %>%                 # Summarizing the number of isolates
  group_by_all() %>%                                              #
  summarize(N = n()) %>%                                          #
  arrange(desc(Country), Region, Source, Year) %>%                # Rearranging rows
  group_by(Country, Region, Source) %>%                           # Collapsing Years and Hosts
  summarize(Year = paste(sort(unique(Year)), collapse = ", "),    #
            Host = paste(sort(unique(Host)), collapse = ", "),    #
            N = sum(N)) %>%                                       #
  arrange(desc(Country), Region, desc(N)) %>%                     # Rearranging rows
  group_by(Country, Region) %>%                                   # Adding blanks in repeated Country and Region Names
  mutate(set_blank = blank_it(Region)) %>%                        #
  ungroup() %>%                                                   #
  mutate(Country = ifelse(set_blank, "", Country)) %>%            #
  mutate(Region = ifelse(set_blank, "", Region)) %>%              #
  select(Country, Region, Source, Year, Host, N) %>%              #
  rename(State = Region) %>%                                      # Renaming columns
  rename(`Field Code` = Source)                                   #
